Manuscript_draft

### 2020-12-16 manuscript_draft.Rmd
manny work

  # Tree heights model
  appNums("heightDiamRawPlot",display=FALSE) # Plot of diameter/heights`

@@

```{r tree level fir spruce contrasts}

@@

trtContrast<-list(
  caption="Contrasts of predicted 1992-2019 tree growth among treatments within each species.  Ratio of predicted growth between treatments is in 'ratio' column.",

# set up the table and place within list  
table=  
  pairs(rg,by=c("Species","Init"),type="response") %>% 
  as.data.frame() %>% 
  mutate(Init=as.numeric(as.character(Init))) %>% # change from factor to numeric
  mutate(Init=ba2d(Init)) %>% # convert basal area to diameter
  arrange(Species,contrast,Init) %>% 
  rename(DBH.1992="Init") %>% 
  mutate_if(is.double,round,5) %>%

  # flextable
  flextable(col_keys = c(colnames(.)[c(2,1,6:8,3:5)])) %>% 
  border_outer(part="all", border = fp_border(color="#2c3a51" , width = 2)) %>% 
  align(align="left",part = "all") %>% 
  vline( border = fp_border(color="#2c3a51" , width = 1), part = "all" ) %>% 
  hline( border = fp_border(color="#2c3a51" , width = 1), part = "all" ) %>% 
  merge_v(j=c(1:2,6:8)) %>% 
  valign(valign="top") %>%
  hline_bottom() %>% 
  fix_border_issues()# border(border.bottom = fp_border(color="black"))

# Close list
) # close list

@@

  figNums(name="treeBAI.plot",display=FALSE)

@@

----------------

`r tableNums("fitBA.table",caption=fitBA.summ$caption)`

```{r present tree growth model summary}

tab_model(fitBA)

---------------------------

```{r display tree growth figure}

treeBAI.plot

`r appNums("sppContrast.table",caption=sppContrast$caption)`

```{r print fir spruce contrasts, ft.align="left"}

# print to screen
sppContrast$table
```

-----------------------

`r appNums("trtContrast.table",caption=trtContrast$caption)`

```{r print treatment contrasts, ft.align="left"}

# print to screen
trtContrast$table

--------------------------

@@

heightDiamRaw.plot<-
  X %>% 
    filter(Species %in% c("Bl","Sx")) %>% # filter for Bl and Sx for now
    filter(Status=="Live") %>% # filter for live trees
    filter(is.na(DBT)) %>% # filter for trees with no broken tops
    drop_na(Height) %>% # remove trees where height was not measured

@@

@@

### Estimating tree height from diameter
Tree heights had a positive nonlinear relationship with diameter, for both species and across all time periods (`r appNums("heightDiamRawPlot",display="cite")`).  A comparison of height-diameter models showed that intercepts and slopes of log-transformed heights did not vary significantly (i.e., p>0.05) between species or time periods (not shown), therefore a single height-diameter linear mixed-effects model was developed using `r X %>% filter(Species %in% c("Fir","Spruce")) %>% filter(Status=="Live") %>% filter(is.na(DBT)) %>% drop_na(Height) %>% nrow()` tree height-diameter observations in the dataset, with log-transformed diameter as the fixed effect, and tree nested within plot as random effects. This model explained `r round(MuMIn::r.squaredGLMM(htDiamFit)[1]*100,1)`% of variation in log-transformed heights, with an intercept of `r round(fixef(htDiamFit)[1],3)` and slope coefficient of  `r round(fixef(htDiamFit)[2],3)` * log-transformed DBH (not shown).  Residual and predicted vs actual height plots were assessed to ensure goodness of fit (`r appNums("htModelFit.plot",display="cite")`). This model was applied to predict heights in trees without height measurements, and tree-volume estimates generated as per Nigh [-@nigh2016].

@@

>>>>

@@

```{r tree level species contrasts}

@@

trtContrast<-
  pairs(rg,by=c("Species","Init"),type="response") %>% 
  as.data.frame() %>% 
  mutate(Init=as.numeric(as.character(Init))) %>% # change from factor to numeric
  mutate(Init=ba2d(Init)) %>% # convert basal area to diameter
  arrange(Species,contrast,Init) %>% 
  rename(DBH.1992="Init")

@@

  figNums(name="treeBAI.plot",display=FALSE) # Estimated marginal means from Lme

@@

@@

@@

# Tree heights model
  appNums("heightDiam.plot",display=FALSE) # Plot of diameter/heights`

@@

### Estimating tree height from diameter
Tree heights had a positive nonlinear relationship with diameter, for both species and across all time periods (`r appNums("heightDiam.plot",display="cite")`).  A comparison of height-diameter models showed that intercepts and slopes of log-transformed heights did not vary significantly (i.e., p>0.05) between species or time periods (not shown), therefore a single height-diameter linear mixed-effects model was developed using `r X %>% filter(Species %in% c("Fir","Spruce")) %>% filter(Status=="Live") %>% filter(is.na(DBT)) %>% drop_na(Height) %>% nrow()` tree height-diameter observations in the dataset, with log-transformed diameter as the fixed effect, and tree nested within plot as random effects. This model explained `r round(MuMIn::r.squaredGLMM(htDiamFit)[1]*100,1)`% of variation in log-transformed heights, with an intercept of `r round(fixef(htDiamFit)[1],3)` and slope coefficient of  `r round(fixef(htDiamFit)[2],3)` * log-transformed DBH (not shown).  Residual and predicted vs actual height plots were assessed to ensure goodness of fit (`r appNums("htModelFit.plot",display="cite")`). This model was applied to predict heights in trees without height measurements, and tree-volume estimates generated as per Nigh [-@nigh2016].

@@

```{r height to diameter plot}

  X %>% 
    filter(Species %in% c("Fir","Spruce")) %>% # filter for Bl and Sx for now
    filter(Status=="Live") %>% # filter for live trees
    filter(is.na(DBT)) %>% # filter for trees with no broken tops
    drop_na(Height) %>% # remove trees where height was not measured

`r appNums("heightDiam.plot",caption="Relationship between height (m) and diameter (cm) for ")`
